### 2014-03-03 seminar/seminar_report/chapter2.tex
changes

\subsection{Web Services}\label{sec:CWSWebServices}
Over the past years, online services have become part of standard
daily life of people around the globe. Many modern applications
rely on web services from different providers. For instance, many
mobile and tablet applications which have limited storage and
processing power are merely interfaces aggregating different
information from online services. Examples are vast, weather
forecasting, ticket selling, shopping apps, local maps and places
searching.

The World Wide Web Consortium (W3C) defines web services as
follows: ``software system designed to support interpretable
machine-to-machine interaction over a network. It has an interface
described in a machine-processable format (specifically WSDL).
Other systems interact with the web service in a manner prescribed
by its description using SOAP messages, typically conveyed using
HTTP with XML serialization in conjunction with other Web-related
standards''. When developers declare a new web service, it will be
discovered based on its description that fully discloses its
functionalities. Developers also have to declare a public
interface and a readable documentation to help other developers
when integrating different services \cite{w3cwsdl}. Nowadays, web
API standards which do not require XML-based web service protocols
like SOAP and WSDL are also emerging. They are also called REST
(representational state transfer) services which are moving
towards simpler communication protocols. %They are not restricted
%to XML formats, recently JSON, a human readable and simpler format
%is becoming popular among online service providers.

We are not going to delve into engineering details of online web
service implementation and its protocols in this proposal. We are
interested in web services from their business model perspective.
Service providers usually charge end users for services they
provide. For example, Google has listed their pricing and plans
for wide range of services they provide on their web service
console page\footnote{https://code.google.com/apis/console}.

@@

        When dealing with cooperative games, two issues need to be
        addressed:\\ 1. Which coalitions among all possible coalitions to form? \\
        2. How to reward each member when a task is completed?\\
        %
        The following sections help address these two issues.

@@

            \subsubsection*{$\epsilon$-core}\label{s:epsilon}
            %\emph{$\epsilon$-Core:}
            %\\
            When the \emph{core} set of a game is empty, it means no coalition
            of players can gain anything by deviating. An outcome would be
            unstable if a coalition can benefit even by a small amount from
            deviating, which is a strong requirement. In fact, in some
            situations, deviations can be costly, or players may have loyalty
            to their coalitions, or even it can be computationally intractable
            to find those small benefits. It would only make sense for a
            coalition to deviate if the gain from a deviation exceeds the cost
            of performing the deviation. \emph{$\epsilon$-core} relaxes the
            notion of the core, and only requires that no coalition would
            benefit significantly, or within a constant amount($\epsilon$) by
            deviating (see Equation \ref{eq:core}).

@@

        In order to make cooperative game concepts practical in real world application, we have proposed an approximation multi-layer
        algorithm useful for service orinted computing settings. Our excrements illustrate, these algorithms can provide
        applicable and near optimal solutions for real world applications.

>>>>

\subsection{Web Services}\label{sec:CWSWebServices}

@@

@@

            %\subsubsection*{$\epsilon$-core}\label{s:epsilon}
%            %\emph{$\epsilon$-Core:}
%            %\\
%            When the \emph{core} set of a game is empty, it means no coalition
%            of players can gain anything by deviating. An outcome would be
%            unstable if a coalition can benefit even by a small amount from
%            deviating, which is a strong requirement. In fact, in some
%            situations, deviations can be costly, or players may have loyalty
%            to their coalitions, or even it can be computationally intractable
%            to find those small benefits. It would only make sense for a
%            coalition to deviate if the gain from a deviation exceeds the cost
%            of performing the deviation. \emph{$\epsilon$-core} relaxes the
%            notion of the core, and only requires that no coalition would
%            benefit significantly, or within a constant amount($\epsilon$) by
%            deviating (see Equation \ref{eq:core}).
%
%            \begin{equation}\label{eq:core2}
%            \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
%            \end{equation}

@@

        In order to make cooperative game concepts practical in real world application, we have proposed an approximation multi-layer
        algorithm useful for service oriented computing settings. Our excrements illustrate, these algorithms can provide
        applicable and near optimal solutions for real world applications.

\subsection{Stability of Coalitions}

Core stability is a highly desirable property however in many problems it is not achievable. It would be more ideal to maintain a set of somewhat stable payoffs when the core is empty. There are several approaches to achieve this goal. One may drop the stability requirement and focus on other types of solutions for which a payoff division is guaranteed to exist. Two well known solution concepts in this category are \emph{nucleolus}\cite{schmeidler_nucleolus_1969} and the \emph{bargaining set}\cite{Davis67existenceof}. They try to minimize some measure of unhappiness in the game for the agents.

Another approach to stabilize the game can be achieved via external subsides. When \emph{Core} is empty it means the game is not stable since the coalition is unable to generate enough revenue to satisfy the demands of each subset of agents. An external party that is interested in stabilizing the game provides a subsidy to the agents if they form the grand coalition, and thus a value of $\lambda v(C)$ is divided among them, where $\lambda \geq 1$. Clearly any game can be stabilized using a large enough $\lambda$, however the external party would be interested in the minimal subsidy required in order to stabilize the game.

A community can also be stabilized by relaxing the core constraints. According to \emph{Core}, an outcome is unstable if a coalition can benefit even by a small amount from deviating, which is a strong requirement. In fact, in some situations, deviations can be costly, or players may have loyalty to their coalitions, or even it can be computationally intractable to find those small benefits. It would only make sense for a coalition to deviate if the gain from a deviation exceeds the cost of performing the deviation. \emph{$\epsilon$-core} relaxes the notion of the core, and only requires that no coalition would benefit significantly, or within a constant amount($\epsilon$) by deviating (see Equation \ref{eq:core}).

Alternatively, the $\epsilon$ can be thought of as a \emph{tax} imposed on a coalition should it choose to deviate. This can again be seen as an external party, trying to stabilize the coalition by imposing some \emph{tax} on deviation. Taxation and subsiding as methods of stabilizing cooperative games have been studied in \cite{RePEc:spr:jogath:v:38:y:2009:i:1:p:3-16, RePEc:mse:cesdoc:12022r, Bachrach:2009:CSC:1692490.1692502, conf/ijcai/MeirRM11}.
